Modal Abstractions for Virtualizing Memory Addresses

### 2025-07-14 examples_C.tex
+

%$\assert{\ulcorner \mathsf{aligned maddr} \urcorner \ast \mathsf{r14} \mapsto_{\textsf{r}} \textsf{r14v} \ast \mathsf{r13} \mapsto_{\textsf{r}} \textsf{maddr} \ast \mathsf{rdi} \mapsto_{\textsf{r}} \textsf{rdiv} \ast \mathsf{rax} \mapsto_{\textsf{r}} \textsf{raxv}}$
%$\assert{\ulcorner \ptablestore !! \textsf{maddr} = \textsf{None} \urcorner \ast \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast \textsf{Pf}} $
\newcommand{\sumwalkabsent}{
  \ownGhost\gammaPred{\authfrag{\singletonMap{\texttt{entry+KERNBASE}}{(\textsf{qfrac}, \textsf{entry})}}}
}

@@

;;pte_t *pte_get_next_table(pte_t *entry) { ... // setting up the stack for a pte_t *next elided

@@

mov    -0x8[rbp],rdi $\specline{\ldots \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{entry} \ast \ldots }$
mov     rdi, r8 $\specline{\ldots \ast \texttt{r8}  \mapsto_{\textsf{r}} \textsf{entry} \ast \ldots }$
mov    [r8],rdi (*\label{line:read_entry_contents}*) $\specline{\ldots \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{entry\_val}  \ast\ldots}$ ;; reading page table entry Justified by virtual pte-pointsto
and    0x1,rdi;  mov    rdi,rax; cmp    0x0,rax ;;  if (!entry->present) {(* \label{line:check_entry_present} *)(* \label{line:mask_present} *)
jne    161 <pte_get_next_table+0xa1> (* \label{line:check_entry_present_jump} *) ;; Jump if the present bit is not zero; no need to allocate next level

@@

mov    rbp,rdi; sub    0x10, rdi ;; Store the value of rbp minus 16 bytes (address of (*\textsf{next}*)) into rdi (*\label{line:pass_addrof_next}*)(*\label{line:alloc_path_start}*)

@@

@@

@@

>>>>

%$\assert{\ulcorner \mathsf{aligned maddr} \urcorner \ast \mathsf{r14} \mapsto_{\textsf{r}} \textsf{r14v} \ast \mathsf{r13} \mapsto_{\textsf{r}} \textsf{maddr} \ast \mathsf{rdi} \mapsto_{\textsf{r}} \textsf{rdiv} \ast \mathsf{rax} \mapsto_{\textsf{r}} \textsf{raxv}}$
%$\assert{\ulcorner \ptablestore !! \textsf{maddr} = \textsf{None} \urcorner \ast \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast \textsf{Pf}} $
\definecolor{main-color}{rgb}{0.6627, 0.7176, 0.7764}
\definecolor{back-color}{rgb}{0.1686, 0.1686, 0.1686}
\definecolor{string-color}{rgb}{0.3333, 0.5254, 0.345}
\definecolor{key-color}{rgb}{0.8, 0.47, 0.196}

\lstdefinestyle{mystyle}
{
    language = C,
    basicstyle = {\footnotesize,\color{black}},
    backgroundcolor = {\color{white}},
    stringstyle = {\color{string-color}},
    keywordstyle = {\color{key-color}},
    keywordstyle = [2]{\color{lime}},
    keywordstyle = [3]{\color{yellow}},
    keywordstyle = [4]{\color{teal}},
    otherkeywords = {;,<<,>>,++},
    morekeywords = [2]{;},
    morekeywords = [3]{<<, >>},
    morekeywords = [4]{++},
    escapeinside={(*}{*)},
}
\newcommand{\sumwalkabsent}{
  \ownGhost\gammaPred{\authfrag{\singletonMap{\texttt{entry+KERNBASE}}{(\textsf{qfrac}, \textsf{entry})}}}
}

@@

\begin{lstlisting}[firstnumber=1, mathescape, language = C, style=mystyle]
pte_t *pte_get_next_table(pte_t *entry) {
  pte_t *next;
  /*setting up the stack for a pte_t *next elided*/

@@

  $\specline{\ldots \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{entry} \ast \ldots }$
  $\specline{\ldots \ast \texttt{r8}  \mapsto_{\textsf{r}} \textsf{entry} \ast \ldots }$
   (*\label{line:read_entry_contents}*)$\specline{\ldots \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{entry\_val}  \ast\ldots}$
   /*reading page table entry Justified by virtual pte-pointsto*/
   if (!entry->present) {/* Jump if the present bit is not zero; no need to allocate next level (* \label{line:check_entry_present} *)(* \label{line:mask_present} *) */

@@

     /*Store the value of rbp minus 16 bytes (address of (*\textsf{next}*)) into rdi (*\label{line:pass_addrof_next}*)(*\label{line:alloc_path_start}*) */

@@

     pte_initialize(entry);(* \label{line:call_to_pte_initialize} *)

@@

     /*... entry value updates:*/
     entry->pfn = nextpaddr; entry->present = 1; (*\label{line:install_new_entry}*)
     /*... now we know that entry is initialized, so we satisfy the condition to access children list */

@@

    } (*\label{line:end_of_allocation_path}*)
   /*...  Code after conditional continued in Figure (*\ref{fig:p2v}*)*/
